Automated Formal Synthesis\\ of Safe Digital Controllers for Continuous Plants

### 2018-05-11 automatica/paper.tex
section 5

%-------------------------------
\subsection{Multi-stage approach} 
\label{sssec:naive}
%-------------------------------

@@

@@

\item The inductive synthesis phase ({\sc synthesize}) uses BMC to compute a
candidate solution $K$ that satisfies both the stability criteria and the
safety specification.  To synthesize a controller that satisfies the
stability criteria, we require that a computed polynomial satisfies Jury's
criterion~\cite{fadali}.  The details of this calculation can be found in
the Appendix.

Regarding the second requirement, we synthesize a safe controller by
unfolding the transition system $k$ steps and by picking a controller $K$
and a single initial state, such that the states at each step do not violate
the safety criteria.  That is, we ask the bounded model checker if there
exists a $K$ that is safe for at least one $x_0$ in our set of all possible
initial states.  This is sound if the current $k$ is greater than the completeness
threshold.  We~also assume some (fixed or floating point) precision $\langle I_p,F_p\rangle$ for the
plant and a sampling rate.  The checks that these assumptions hold are
performed by subsequent {\sc verify} stages.

@@

\item The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps where we assume $k$ to be under the
completeness threshold.  After unfolding the transition system corresponding
to the previously synthesized controller $k$ steps, we check that the safety
specification holds for any initial state. This is shown in Alg.~~\ref{alg:safetycheck}.

@@

\item The third {\sc verify} stage, {\sc complete}, checks that the current
$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate controller $K$ and
check that $k{\geq}\overline{k}$.  This is done according to the argument
given above and illustrated in Fig.~\ref{fig:ct}.

@@

Checking that the safety specification holds for any initial state can be
computationally expensive if the bounds on the allowed initial states are
large.

@@

Essentially, this approach relies on the symbolic simulation over a bounded
time horizon of individual initial states and inputs that form part of an
uncountable space and tries to generalize it for an infinite space over an
infinite time horizon.

>>>>

%-------------------------------
\subsection{Multi-stage CEGIS} 
\label{sssec:naive}
%-------------------------------

@@

\note{we need to refer to the parts of Algorithm 1 more closely - point to specific lines in the explanation below.}

@@

\item The inductive synthesis phase ({\sc synthesize}) uses BMC to compute a
candidate solution $K$ that satisfies both the stability criteria and the
safety specification.

To synthesize a controller that satisfies the
stability criteria, we require that a computed polynomial satisfies Jury's
criterion~\cite{fadali} \note{use specific formula}.  The details of this calculation can be found in
the Appendix.

Regarding the second requirement, 
we fix an index $k$, 
and we synthesize a safe controller by
unfolding the transition system $k$ steps and by selecting a controller $K$ and a single initial state, 
such that the states at each step do not violate the safety criteria \note{use specific formula}.  
That is, we ask the bounded model checker \note{have we discussed the BMC earlier?} if there exists a $K$ that is safe for at least one $x_0$ in our set of all possible initial states.  
This is sound if the current $k$ is greater than the completeness threshold (see later step).  
We~also assume some (fixed or floating point) precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  
The checks that these assumptions hold are performed by subsequent {\sc verify} stages. 
\note{we have not discussed the bounds on the input signal. }

@@

\item The first {\sc verify} stage, {\sc safety}, checks that the candidate
solution $K$, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps \note{where we assume $k$ to be under the
completeness threshold}.  After unfolding the transition system corresponding
to the previously synthesized controller $k$ steps, we check that the safety
specification holds for any initial state. This is shown in Alg.~~\ref{alg:safetycheck}.

@@

\item The third {\sc verify} stage, {\sc complete}, checks that the current
$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate controller $K$ and
check that $k{\geq}\overline{k}$.  This is done according to the argument
given above and illustrated in Fig.~\ref{fig:ct}. 
\note{it is not clear how we find $\overline{k}$.}

@@

Checking that the safety specification holds for any initial state can be
computationally expensive if the bounds on the allowed initial states are
large. \note{we have not discussed the bounds on the input signal. }

@@

This approach relies on the symbolic simulation over a bounded
time horizon of individual initial states and inputs that form part of an
uncountable space and tries to generalize it for an infinite space over an
infinite time horizon.
